bracer
======

[![CRAN Status Badge](https://www.r-pkg.org/badges/version/bracer)](https://cran.r-project.org/package=bracer)
[![R-CMD-check](https://github.com/trevorld/bracer/workflows/R-CMD-check/badge.svg)](https://github.com/trevorld/bracer/actions)
[![Coverage Status](https://codecov.io/github/trevorld/bracer/branch/master/graph/badge.svg)](https://app.codecov.io/github/trevorld/bracer?branch=master)

### Table of Contents

* [Overview](#overview)
* [Examples](#examples)
* [Installation](#installation)
* [Limitations of pure R parser and alternative javascript parser](#limitations)

## <a name="overview">Overview</a>

``{bracer}`` provides support for performing [brace expansions](https://www.gnu.org/savannah-checkouts/gnu/bash/manual/bash.html#Brace-Expansion) on strings in R.

## <a name="examples">Examples</a>

```{r examples}
library("bracer")
options(bracer.engine = "r")
expand_braces("Foo{A..F}")
expand_braces("Foo{01..10}")
expand_braces("Foo{A..E..2}{1..5..2}")
expand_braces("Foo{-01..1}")
expand_braces("Foo{{d..d},{bar,biz}}.{py,bash}")
```

``expand_braces()`` is vectorized and returns one big character vector of all the brace expansions.  ``str_expand_braces()`` is an alternative that returns a list of character vectors.

```{r vectorized}
expand_braces(c("Foo{A..F}", "Bar.{py,bash}", "{{Biz}}"))
str_expand_braces(c("Foo{A..F}", "Bar.{py,bash}", "{{Biz}}"))
```

``glob()`` is a wrapper around ``Sys.glob()`` that uses ``expand_braces()`` to support both brace and wildcard expansion on file paths.

```{r glob}
glob("R/*.{R,r,S,s}")
```

## <a name="installation">Installation</a>

To install the release version on CRAN use the following command in R:

```{r install_stable, eval=FALSE}
install.packages("bracer")
```

To install the developmental version use the following command in R:

```{r install, eval=FALSE}
remotes::install_github("trevorld/bracer")
```

Installing the suggested ``{V8}`` package will enable use of the javascript alternative parser:

```{r install_v8, eval=FALSE}
install.packages("V8")
```

## <a name="limitations">Limitations of pure R parser and alternative javascript parser</a>

The ``{bracer}`` pure R parser currently does not properly support the "correct" (Bash-style) brace expansion under several edge conditions such as:

1. Unbalanced braces e.g. ``{{a,d}`` (but you could use an escaped brace instead ``\\{{a,d}``)
2. Using surrounding quotes to escape terms e.g. ``{'a,b','c'}`` (but you could use an escaped comma instead  ``{a\\,b,c}``)
3. Escaped braces within comma-separated lists e.g. ``{a,b\\}c,d}``
4. (Non-escaping) backslashes before braces e.g. ``{a,\\\\{a,b}c}``
5. Sequences from letters to non-letter ASCII characters e.g. ``X{a..#}X``

```{r r_engine}
options(bracer.engine = "r")
expand_braces("{{a,d}")
expand_braces("{'a,b','c'}")
expand_braces("{a,b\\}c,d}")
expand_braces("{a,\\\\{a,b}c}")
expand_braces("X{a..#}X")
```

However if the ``{V8}`` suggested R package is installed we can instead use an embedded version of the [braces](https://github.com/micromatch/braces) Javascript library which can correctly handle these edge cases.  To do so we need to set the bracer "engine" to "v8".

```{r v8_engine}
options(bracer.engine = "v8")
expand_braces("{{a,d}")
expand_braces("{'a,b','c'}")
expand_braces("{a,b\\}c,d}")
expand_braces("{a,\\\\{a,b}c}")
expand_braces("X{a..#}X")
```
